AusTraits -- a curated plant trait database for the Australian flora

### 2020-11-03 ms.Rmd
Consolidate dataset constructionm package loading

```{r, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
library(knitr)
library(tidyverse)
library(rmarkdown)
source("R/ms.R")
source("R/load_data.R")
load_data()

@@

```{r}

## Add `\citet{}` for references. 
## Separate into groups of max size n. 
## This is needed for latex table, overwise citations
## spill off the page
format_cites_n <- function(x, n = 6){

  # Make sorted vector of all unique refs
  x2 <- str_split(x, ", ") %>% unlist() %>% sort()
  # Make a vector with group ids for references
  groups <- (rep(1:ceiling(length(x2)/n), n) %>% sort() )[seq_len(length(x2))]

  ## wrap given txt with citation call  
  format_cites_sub <- function(x) {x %>% paste(collapse = ", ") %>% paste0("\\citep{", ., "}" )}

  ## split into groups of n citations, wrap each with citation call, the combine
  split(x2, groups) %>% lapply(format_cites_sub) %>% paste(collapse = " \\newline ")
  }

## format table
make_latex_table <- function(data) {
  data %>%
  # nasty hacks - replace `_` with `TTTTT` then return below, prevents unhelpful handling of _ in creation of latex table
  mutate(refs = str_replace_all(refs, "_", "TTTT")) %>%  
  knitr::kable("latex",  booktabs = TRUE, longtable = TRUE ) %>%
  kableExtra::kable_styling(font_size = 7, latex_options = c("repeat_header", "striped")) %>%
  kableExtra::column_spec(1, width = "3cm") %>%
  kableExtra::column_spec(2, width = "4cm") %>%
  kableExtra::column_spec(9, width = "3cm") %>%
  kableExtra::add_header_above(c(" ", " ", " ", "Number of records" = 5)) %>%
  # nasty hacks - clean up backslashes and references. (why oh why is this needed?)
  str_replace_all(fixed("textbackslash{}"), fixed("")) %>%
  str_replace_all(fixed("gray!6"), fixed("gray!20")) %>%
  str_replace_all(fixed("\\{"), fixed("{")) %>%
  str_replace_all(fixed("\\}"), fixed("}"))  %>% 
  str_replace_all(fixed("TTTT"), fixed("_")) %>%
  str_split("\\n") %>% unlist()
}

# wraps text in table cell to max number of characters per line -- needed for long words with no spaces (i.e. trait names)
txt_wrap <- function(txt, n=22) {

  f <- function(txt, end=-1L) {
      ifelse(str_length(txt) > 0, paste("\\newline", str_sub(txt, 0, end)), txt)
  }

  g <- function(txt) {
      ifelse(str_length(txt) < n, -1L, 
              str_locate_all(txt,"_") %>% purrr::map_dbl(~.x %>% .[,"start"] %>% subset(., .<= n) %>% max(., -1L)) 
            )
  }

  i <- g(txt)
  txt2 <- ifelse(str_length(txt) > n , str_sub(txt, i+1), "")
  ii <- g(txt2)
  txt3 <- ifelse(str_length(txt2) > n , str_sub(txt2, ii+1), "")

  paste(str_sub(txt, 1, i), f(txt2, ii), f(txt3))
}

n_records %>%
  mutate(
         Trait = txt_wrap(Trait),
         Group = paste0(str_to_sentence(Tissue), " (", Category, ")") %>%  str_replace_all("_", " "), 
         Type = ifelse(Type=="numeric", "num.", Type),
         Type = ifelse(Type=="categorical", "cat.", Type),
         Type = ifelse(Type=="character", "chr.", Type),
         refs = purrr::map_chr(refs, format_cites_n),
         ) %>%
  select(-Tissue, -Category) %>%
  select(Group, everything()) %>%
  nest(data = -Group) %>% 
  mutate(
    ## turn each group into table
    tex = purrr::map(data, make_latex_table),
    ## drop top and bottom of each table
    tex_sub =  purrr::map2_chr(tex, Group, ~c(sprintf("\\multicolumn{3}{l}{{\\bf %s}}\\\\", .y),.x[ seq(1 + which(grepl("endlastfoot", .x)), -1 + which(grepl("end{longtable}", .x, fixed=TRUE)))], "\\\\ \\midrule \n  \\\\ \n ") %>% paste(collapse = "\n")) 
    ) -> x

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
devtools::load_all()
source("R/ms.R")
source("R/load_data.R")
load_data()

@@

```{r}
 n_records %>%
  mutate(
         Trait = txt_wrap(Trait),
         Group = paste0(str_to_sentence(Tissue), " (", Category, ")") %>%  str_replace_all("_", " "), 
         Type = ifelse(Type=="numeric", "num.", Type),
         Type = ifelse(Type=="categorical", "cat.", Type),
         Type = ifelse(Type=="character", "chr.", Type),
         refs = purrr::map_chr(refs, format_cites_n),
         ) %>%
  select(-Tissue, -Category) %>%
  select(Group, everything()) %>%
  nest(data = -Group) %>% 
  mutate(
    ## turn each group into table
    tex = purrr::map(data, make_latex_table),
    ## drop top and bottom of each table
    tex_sub =  purrr::map2_chr(tex, Group, ~c(sprintf("\\multicolumn{3}{l}{{\\bf %s}}\\\\", .y),.x[ seq(1 + which(grepl("endlastfoot", .x)), -1 + which(grepl("end{longtable}", .x, fixed=TRUE)))], "\\\\ \\midrule \n  \\\\ \n ") %>% paste(collapse = "\n")) 
    ) -> x
